Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
change wording.

Unfortunately, the strong type system of Haskell does not guarantee
no value errors.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test programs than programmers of other
programming languages.

TBD: we need evidence to support above.

@@

We can see the equation as a boolean property for {\tt null} and {\tt empty} and
can say that there are potentially demands to show properties with Haddock annotation.
To our experience, it is not difficult to find properties for pure functions.
We believe that Haskellers should show properties of pure functions
in documentation.

But there is no annotation syntax to describe properties in Haddock.
Even if a prefix keyword for properties is defined, 
we have no agreement on how to describe non-boolean properties: e.g. how to specify types of funcation parameters. And we don't have automatic test mechanism to use properties in documentation.

Note that QuickCheck 2.3 or earlier tests a boolean property 100 times though just one test is enough. (should got to appendix?)

@@

There are some examples and properties which are not useful for users but useful for developers. One example is a corner case registered in a bug track system. We don't have a mechanism to integrate design, documentation and tests.

@@

TBD: talk about exception.

To specify properties in haddock annotations, we propose a new syntax. In this paper, we use the {\tt prop>} prefix. We can write the boolean equation as follows:

@@

\noindent talk about how to specify non-boolean properties.

@@

\noindent talk about open lambda term.

@@

@@

%% \appendix
%% \section{Appendix Title}

%% This is the text of the appendix, if you need one.

@@

We would like to thank
Nick Smallbone for having improved QuickCheck so that boolean property is tested
just once.
We are grateful to David Waern and Simon Marlow
for introducing the property syntax to Haddock.

>>>>

Unfortunately, the strong type system of Haskell does not guarantee
no value errors.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test programs than programmers of other
programming languages. TBD: we need evidence to support this.

@@

We can see the equation as a no-parameter property for {\tt null} and {\tt empty} and
can say that there are potentially demands to show properties with Haddock annotation.
To our experience, it is not difficult to find properties for pure functions.
We believe that Haskellers should show properties of pure functions
in documentation.

But there is no annotation syntax to describe properties in Haddock.
Even if a prefix keyword for properties is defined, 
we have no agreement on how to describe parameterized properties: e.g. how to specify types of funcation parameters. And we don't have automatic test mechanism to use properties in documentation.

@@

There are some examples and properties which are not useful for users but useful for developers. One example is a corner case registered in a bug track system. TBD: setup-teardown. We don't have a mechanism to integrate design, documentation and tests.

@@

TBD: command and library. 
TBD: talk about exception.

To specify properties in haddock annotations, we propose a new syntax. In this paper, we use the {\tt prop>} prefix. We can write the no-parameter equation as follows:

@@

\noindent Of course, we allowed parameterized properties by
using closed lambda terms.
Type signatures can be specified for each parameter:

@@

\noindent Since the right hand side of {\tt ->} is verbose as documentation,
open lambda terms are also allowed:

@@

\noindent To test properties in haddock annotations, we extended doctest to handle
them with QuickCheck.

@@

\appendix

\section{Package Survey}

TBD

\section{Improving QuickCheck}

Since no-parameter properties has no parameters, it is enough to test them
just one.
However, QuickCheck 2.3 or earlier tests no-parameter properties 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
This will be fixed in the next release of QuickCheck.

@@

We would like to thank
Nick Smallbone for having improved QuickCheck so that no-parameter properties are tested just once.
We are grateful to David Waern and Simon Marlow
for introducing the property syntax to Haddock.
